---
title: "npp-transect-eml-assembly"
author: "Kate Morkeski"
date: "3/3/2022"
output: html_document
---

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Load required packages

# two of the required packages are installed from GitHub
# uncomment these lines to update as needed
# library(remotes)
# remotes::install_github("EDIorg/EMLassemblyline")
# remotes::install_github("WHOIGit/ediutilities")

library(EMLassemblyline)
library(ediutilities)
library(here)
library(tidyverse)
library(readxl)
library(lubridate)
library(devtools)
library(EML)
library(maps)
library(xml2)
library(geosphere)
library(httr)
library(compareDF)

# Set path to root of project
here("nes-lter-npp-transect")

```

## Read in provided data

```{r}

# identify version
# version1 input data August 2019-February 2020
# version2 input data July-October 2020
#version <- 'version1'
version <- 'v2'

if (version == 'version1') {
npp_discrete <- read_csv(paste0('npp_discrete_', version, '.csv'), show_col_types = FALSE) 
npp_integrated <- read_csv(paste0('npp_integrated_', version, '.csv'), show_col_types = FALSE) 
}

# combine before or after QA steps? 
if (version == 'v2') {
npp_discrete_1 <- read_csv(paste0('npp_discrete_version1.csv'), show_col_types = FALSE) 
npp_discrete_2 <- read_csv(paste0('npp_discrete_version2.csv'), show_col_types = FALSE) 
npp_discrete <- rbind(npp_discrete_1, npp_discrete_2)
npp_integrated_1 <- read_csv(paste0('npp_integrated_version1.csv'), show_col_types = FALSE) 
npp_integrated_2 <- read_csv(paste0('npp_integrated_version2.csv'), show_col_types = FALSE) 
npp_integrated <- rbind(npp_integrated_1, npp_integrated_2) 
write.csv(npp_discrete, "nes-lter-npp-transect-discrete-v2.csv", row.names = FALSE)
write.csv(npp_integrated, "nes-lter-npp-transect-integrated-v2.csv", row.names = FALSE)
}


```

## Provide summary statistics

```{r}

npp_discrete$cruise <- as.factor(npp_discrete$cruise)
npp_discrete$cast <- as.factor(npp_discrete$cast)
npp_discrete$niskin <- as.factor(npp_discrete$niskin)
npp_discrete$iode_quality_flag <- as.factor(npp_discrete$iode_quality_flag)
npp_discrete$alternate_sample_category <- as.factor(npp_discrete$alternate_sample_category)
npp_discrete$depth_category <- as.factor(npp_discrete$depth_category)
npp_discrete$filter_size <- as.factor(npp_discrete$filter_size)
npp_discrete$percent_surface_irradiance <- as.factor(npp_discrete$percent_surface_irradiance)

npp_integrated$cruise <- as.factor(npp_integrated$cruise)
npp_integrated$station <- as.factor(npp_integrated$station)
npp_integrated$cast <- as.factor(npp_integrated$cast)
npp_integrated$filter_size <- as.factor(npp_integrated$filter_size)
npp_integrated$iode_quality_flag <- as.factor(npp_integrated$iode_quality_flag)
npp_integrated$daytime_Y_N <- as.factor(npp_integrated$daytime_Y_N)

summary(npp_discrete)
summary(npp_integrated)

```

## Plot values to confirm flags and complete a visual inspection

```{r}

ggplot(npp_discrete, aes(x=as.factor(iode_quality_flag), y=npp_rate)) + 
   geom_boxplot() + xlab('iode_quality_flag')

ggplot(npp_discrete, aes(x= date_time_utc, y = npp_rate, color = depth_category))+ geom_point()

ggplot(npp_integrated, aes(x=as.factor(iode_quality_flag), y=integrated_npp_mg_m2_day)) + 
   geom_boxplot() + xlab('iode_quality_flag')

ggplot(npp_integrated, aes(x= date_time_utc, y = integrated_npp_mg_m2_day, color = daytime_Y_N))+ geom_point()

ggplot(npp_integrated, aes(x=as.factor(iode_quality_flag), y=k_meas_per_m)) + 
   geom_boxplot() + xlab('iode_quality_flag')

ggplot(npp_integrated, aes(x=as.factor(iode_quality_flag), y=beam_atten_0_10)) + 
   geom_boxplot() + xlab('iode_quality_flag')

ggplot(npp_integrated, aes(x=as.factor(iode_quality_flag), y=k_calc_per_m)) + 
   geom_boxplot() + xlab('iode_quality_flag')


```

## Plot sampling locations and complete a visual geographic inspection

```{r}

map_locs(npp_integrated, colorvar = "integrated_npp_mg_m2_day", region = "transect")
map_locs(npp_discrete, colorvar = "npp_rate", region = "transect")

```
## Create package data files if any changes to csvs

```{r}



```

## EML Assembly

# Read data table if needed
# identify date column for ediutilities package to generate temporal coverage
# Read the Excel metadata template and generate text templates used by EMLassemblyline


```{r}

excel_template <- 'npp-transect-info.xlsx'

if (version == 'version1') {
sheet_to_tsv(excel_template, 'ColumnHeadersDiscrete', paste0('attributes_npp_discrete_', version, '.txt'))  
sheet_to_tsv(excel_template, 'ColumnHeadersIntegrated', paste0('attributes_npp_integrated_', version, '.txt'))
sheet_to_tsv(excel_template, 'CategoricalVariables', paste0('catvars_npp_discrete_', version, '.txt'))
sheet_to_tsv(excel_template, 'CategoricalVariables', paste0('catvars_npp_integrated_', version, '.txt'))
}

if (version == 'v2') {
sheet_to_tsv(excel_template, 'ColumnHeadersDiscrete', paste0('attributes_nes-lter-npp-transect-discrete-', version, '.txt'))  
sheet_to_tsv(excel_template, 'ColumnHeadersIntegrated', paste0('attributes_nes-lter-npp-transect-integrated-', version, '.txt'))
sheet_to_tsv(excel_template, 'CategoricalVariables', paste0('catvars_nes-lter-npp-transect-discrete-', version, '.txt'))
sheet_to_tsv(excel_template, 'CategoricalVariables', paste0('catvars_nes-lter-npp-transect-integrated-', version, '.txt'))
}

sheet_to_tsv(excel_template, 'Personnel', 'personnel.txt')

sheet_to_tsv(excel_template, 'Keywords', 'keywords.txt')

sheet_to_tsv(excel_template, 'CustomUnits', 'custom_units.txt')

```

Use templates in "template core metadata" step from EML assembly line

```{r}

EMLassemblyline::template_core_metadata(path=here(), license='CCBY')

```

Generate the package and insert the parent project node into the resulting EML

```{r}

 if (version == 'version1') {
   pkg_id <- 'knb-lter-nes.16.1'
   datatables <- c('npp_discrete_version1.csv', 'npp_integrated_version1.csv')
   other <- c('raw_npp_data_version1.zip','HOBO_data.zip', 'light_data.zip')
   parent_project <- 'parent_project_LTER.txt'
   } 

if (version == 'v2') {
  pkg_id <- 'knb-lter-nes.16.2'
  datatables <- c('nes-lter-npp-transect-discrete-v2.csv', 'nes-lter-npp-transect-integrated-v2.csv')
  other <- c('raw_npp_data_version2.zip','HOBO_data.zip', 'light_data.zip')
  parent_project <- 'parent_project_LTER_RAPID.txt'
  }

make_eml(here(),
         dataset.title='Size-fractionated net primary productivity (NPP) estimates based on 13C uptake during cruises along the Northeast U.S. Shelf Long Term Ecological Research (NES-LTER) Transect, ongoing since 2019', 
         data.table= datatables,  
         data.table.description= c('Discrete net primary productivity data', 'Integrated net primary productivity data'),
         data.table.name = name <- c('Discrete NPP', 'Integrated NPP'),
         other.entity = other,
         other.entity.name = c('Raw NPP data table','Raw temperature data files', 'Percent surface irradiance data'),
         other.entity.description = c('Raw data used to generate product data tables', 'Raw incubation tank water temperature data', 'Percent surface irradiance data for each Niskin'),
         temporal.coverage = temporal_coverage(append(npp_discrete$date_time_utc, npp_integrated$date_time_utc)),
         geographic.description = "NES-LTER",
         geographic.coordinates = geographic_coordinates(npp_discrete$latitude, npp_discrete$longitude),
         maintenance.description = "ongoing",
         user.id = "NES",
         user.domain = "LTER",
         package.id = pkg_id)
 
project_insert(pkg_id, parent_project)

```
